A multinomial spatio-temporal model for sexual risk behaviour in AGYW

### 2022-09-17 src/docs_09-09-21-three-category/09-09-21-three-category.Rmd
three-category presentation upload

1. Usual high variance from low counts problem, improved by spatio-temporal smoothing
2. The raw proportions don't add up to one
  * This is illustrated in the next slide

:::: columns

::: column

```{r echo=FALSE}
knitr::include_graphics("page1-check100.pdf")
```

:::

::: column

```{r echo=FALSE}
knitr::include_graphics("page2-check100.pdf")
```

:::

::::

@@

:::: columns

::: column

```{r echo=FALSE}
knitr::include_graphics("page-multi-sexbehav-sae.pdf")
```

:::

::: column

* A (difficult to see) example of what this looks like
* Model 9 has BYM2 and AR1
* Other notes
  * Quantiles produced by manipulating `inla.posterior.sample`s
  * Same samples used in combination with Naomi population data to produce aggregates (i.e. 15-24 age category)

:::

::::

@@

```{r echo=FALSE}
knitr::include_graphics("depends/sexpaid-survey-question.pdf")
```

>>>>

1. Usual high variance from low counts problem, improved by spatio-temporal smoothing
2. The raw proportions don't add up to one

@@

@@
